---
title: "XJ"
output: html_document
---

### load in data

```{r}
data_format <- dataset <- read_csv("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/Harvard_CAS_1993/DS0001/Data_Format_93.csv")

dat93 = read.fwf("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/Harvard_CAS_1993/DS0001/06577-0001-Data.txt", widths=data_format$Col_Width, na.strings=c("NA", " ", "."), col.names = paste0(data_format$Name) )
save(dat93, file="data_1993.rdata")
#------------------------------
data_format <- dataset <- read_csv("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/Harvard_CAS_1997/DS0001/Data_Format_97.csv")

dat97 = read.fwf("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/Harvard_CAS_1997/DS0001/03163-0001-Data.txt", widths=data_format$Col_Width, na.strings=c("NA", " ", "."), col.names = paste0(data_format$Name) )
save(dat97, file="data_1997.rdata")
#------------------------------
data_format <- dataset <- read_csv("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/Harvard_CAS_1999/DS0001/Data_Format_99.csv")

dat99 = read.fwf("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/Harvard_CAS_1999/DS0001/03818-0001-Data.txt", widths=data_format$Col_Width, na.strings=c("NA", " ", "."), col.names = paste0(data_format$Name) )
save(dat99, file="data_1999.rdata")

#-------------------------------
data_format <- dataset <- read_csv("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/Harvard_CAS_2001/DS0001/Data_Format_01.csv")

dat01 = read.fwf("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/Harvard_CAS_2001/DS0001/04291-0001-Data.txt", widths=data_format$Col_Width, na.strings=c("NA", " ", "."), col.names = paste0(data_format$Name) )
save(dat01, file="data_2001.rdata")
```

--------------------- No need to run lines above

```{r message=FALSE,warning=FALSE}
library(readr)
library(visdat)
library(ggpubr)
library(naniar)
library(dplyr)
library(corrplot)
library(ggplot2)
library(ggthemes)
library(wordcloud)
library(BAS)
library(MASS)
library(ggmosaic)
load("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/data_1993.rdata")
load("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/data_1997.rdata")
load("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/data_1999.rdata")
load("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/data_2001.rdata")
```

### EDA (start with 93)

```{r}
dat93_subset<- dat93 %>% dplyr::select(c(A1, A2, A3, A4, A5, A6, A7, A8, A9_C, A9_E, C1_A, C1_B, C7, C8, C9, E1_A, E1_M, F5, G1, G2, G3, G4, G5, G6, G7, G8, G9, G10, G11, G12, G13, G14, G15))
save(dat93_subset, file="data93_subset.rdata")
```

### missing data and data cleaning
------------------------------------------------
### age, maybe not using this in the model, cuz year in school tells all
### gender 37 missing
### year in school 56 missing
### transfer 47 missing
### where live 57 missing
### whom live 57 missing
### major 178 missing
### frat or soro member 59 missing
### academic importance 92 missing
### religion importance 111 missing
### prohibit drinking health 206 missing
### prohibit drinking religious 201 missing
----------------------------------------------
c7-c9, missing might be never drinking, then change missing to 0
-----------------------------------------
### drug use:marijuana 58 missing
### drug use:cigarettes 77 missing
### GPA 69 missing
---------------------------------- ALL G's 
### marital status 86 missing
### span/hispanic 115 missing
### race 222 missing
### religion 174 missing
### health status 96 missing
### weight 222 missing
### height 337 missing 
### last year freq 150 missing
### last year quantity 113 missing
### binge 109 missing
### father alcohol use 214 missing
### mother alcohol use 157 missing
### family attitude 126 missing
### father's edu 50 missing
### mother's edu 41 missing

```{r}
dat93_subset$A2<- as.factor(dat93_subset$A2)
dat93_subset$A3<- as.factor(dat93_subset$A3)
dat93_subset$A4<- as.factor(dat93_subset$A4)
dat93_subset$A5<- as.factor(dat93_subset$A5)
dat93_subset$A6<- ifelse(dat93_subset$A6 > 5, 6, dat93_subset$A6) ### who are you currently living with? (6 indicates others)
dat93_subset$A6<- as.factor(dat93_subset$A6)
dat93_subset$A7<- as.factor(dat93_subset$A7)
dat93_subset$A8<- as.factor(dat93_subset$A8)
dat93_subset$A9_C<- as.factor(dat93_subset$A9_C)
dat93_subset$A9_E<- as.factor(dat93_subset$A9_E)
dat93_subset$C1_A<- as.factor(dat93_subset$C1_A)
dat93_subset$C1_B<- as.factor(dat93_subset$C1_B)
# ------------------------------------------
dat93_subset$num_of_drinks = dat93_subset$C7 * dat93_subset$C8
dat93_subset$C7[is.na(dat93_subset$C7)] = 0
dat93_subset$C7<- as.factor(dat93_subset$C7)
dat93_subset$C8[is.na(dat93_subset$C8)] = 0
dat93_subset$C8<- as.factor(dat93_subset$C8)
dat93_subset$C9[is.na(dat93_subset$C9)] = 0
dat93_subset$C9<- as.factor(dat93_subset$C9)

# -----------------------------------------
dat93_subset$E1_A<- as.factor(dat93_subset$E1_A)
dat93_subset$E1_M<- as.factor(dat93_subset$E1_M)
dat93_subset$F5<- as.factor(dat93_subset$F5)

dat93_subset$G1<- as.factor(dat93_subset$G1)
dat93_subset$G2<- as.factor(dat93_subset$G2)
dat93_subset$G3<- as.factor(dat93_subset$G3)
dat93_subset$G4<- as.factor(dat93_subset$G4)
dat93_subset$G5<- as.factor(dat93_subset$G5)
dat93_subset$G8<- as.factor(dat93_subset$G8)
dat93_subset$G9<- as.factor(dat93_subset$G9)
dat93_subset$G10<- as.factor(dat93_subset$G10)
dat93_subset$G11<- as.factor(dat93_subset$G11)
dat93_subset$G12<- as.factor(dat93_subset$G12)
dat93_subset$G13<- as.factor(dat93_subset$G13)
dat93_subset$G14<- as.factor(dat93_subset$G14)
dat93_subset$G15<- as.factor(dat93_subset$G15)

### c7, fequency 30 days, could do classification, and take c9 into account, then we could create our own variable saying that the ratio of drunk

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(A2, C7), fill=A2), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "Gender")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(A3, C7), fill=A3), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "Year in school")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(A4, C7), fill=A4), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "tansfer")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(A5, C7), fill=A5), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "where live")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(A6, C7), fill=A6), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "whom live")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(A7, C7), fill=A7), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "major")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(A8, C7), fill=A8), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "frat or soro member")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(A9_C, C7), fill=A9_C), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "importance of academic work")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(A9_E, C7), fill=A9_E), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "importance of religion")

# ------------------------------------------
ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(C1_A, C7), fill=C1_A), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "prohibit drinking health")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(C1_B, C7), fill=C1_B), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "prohibit drinking religion")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(E1_A, C7), fill=E1_A), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "drug use:marijuana")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(E1_M, C7), fill=E1_M), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "drug use:cigarettes")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(F5, C7), fill=F5), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "gpa")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G1, C7), fill=G1), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "marital status")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G2, C7), fill=G2), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "span/hispanic")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G3, C7), fill=G3), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "race")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G4, C7), fill=G4), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "religion")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G5, C7), fill=G5), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "health status")

ggplot(dat93_subset, aes(x = C7, y = G6)) +
geom_boxplot() + coord_flip() ### interaction with gender

ggplot(dat93_subset, aes(x = C7, y = G7)) +
geom_boxplot() + coord_flip()

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G8, C7), fill=G8), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "last year freq")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G9, C7), fill=G9), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "last year quantity")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G10, C7), fill=G10), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "binge")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G11, C7), fill=G11), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "father alcohol use")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G12, C7), fill=G12), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "mother alcohol use")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G13, C7), fill=G13), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "family attitude")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G14, C7), fill=G14), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "father's edu")

ggplot(data = dat93_subset) +
   geom_mosaic(aes(x = product(G15, C7), fill=G15), na.rm=TRUE)+
  labs(x = "Freq 30 days", y = "mother's edu")

### hist for num of drinking
### mean and variance
### correlation plot
### maybe use num drinking as response and replot the mosiac


```

```{r}
#save(df, file="df.rdata")

df_simple<- data.frame(df$drinks_binary)
#df_simple$drinks_binary<- df$drinks_binary
df_simple$num_of_drinks<- df$num_of_drinks
df_simple$age<- factor(as.matrix(df[,c(3:6)])%*% 1:4, labels = colnames(df[,c(3:6)]))
df_simple$gender<- df$gender
df_simple$year_in_school<- df$year_in_school

df_simple$subfree_on_housing<- df$subfree_on_housing
df_simple$on_housing<- df$on_housing
df_simple$off_housing<- df$off_housing

df_simple$housing<- factor(as.matrix(df[,c(9:11)])%*% 1:3, labels = colnames(df[,c(9:11)]))

#df[, -(df$no_roommate + df$roommate + df$weird_roomate == 0)]
df_simple$roommate<- factor(as.matrix(df[,c(12:14)])%*% 1:3, labels = colnames(df[,c(12:14)]))

df_simple<- cbind(df_simple, df[,15:23])
df_simple$happy<- factor(as.matrix(df[,c(24:26)])%*% 1:3, labels = colnames(df[,c(24:26)]))
df_simple$gpa<- df$gpa
df_simple$marital<- factor(as.matrix(df[,c(28:31)])%*% 1:4, labels = colnames(df[,c(28:31)]))
df_simple$race<- factor(as.matrix(df[,c(32:37)])%*% 1:6, labels = colnames(df[,c(32:37)]))
df_simple$religion<- factor(as.matrix(df[,c(38:43)])%*% 1:6, labels = colnames(df[,c(38:43)]))
df_simple<- cbind(df_simple, df[,44:48])
df_simple$max_par_edu<- factor(as.matrix(df[,c(49:53)])%*% 1:5, labels = colnames(df[,c(49:53)]))

save(df_simple, file="df_simple.rdata")
#-----------------------------plots in slides and write-up
# ggplot(subset(df_simple,!is.na(roommate)), aes(x=roommate, y=num_of_drinks, fill=roommate)) + 
#     geom_boxplot()+
#   scale_fill_discrete(name="Roommate")+
#   labs(x = "Roommate", y = "Number of drinks per month")

ggplot(df_simple, aes(x=num_of_drinks)) + 
  geom_density()+
  labs(x="Number of drinks per month")

ggplot(subset(df_simple,!is.na(race)), aes(x=race, y=num_of_drinks, fill=race)) + 
    geom_boxplot()+
  scale_fill_discrete(name="Race")+
  labs(x = "Race", y = "Number of drinks per month")+
  scale_y_continuous(limits=c(0,100))
  
### comparison
ggplot(subset(df_simple,!is.na(prohib_medical)), aes(x=as.factor(prohib_medical), y=num_of_drinks, fill=as.factor(prohib_medical))) + 
    geom_boxplot()+
  scale_fill_discrete(name="prohib_medical")+
  labs(x = "Does medical conditions prohibit your drinking?", y = "Number of drinks per month")+
  scale_y_continuous(limits=c(0,100))

ggplot(subset(df_simple,!is.na(prohib_religion)), aes(x=as.factor(prohib_religion), y=num_of_drinks, fill=as.factor(prohib_religion))) + 
    geom_boxplot()+
  scale_fill_discrete(name="prohib_religion")+
  labs(x = "Does religious reasons prohibit your drinking?", y = "Number of drinks per month")+
  scale_y_continuous(limits=c(0,100))

ggplot(subset(df_simple,!is.na(tobac)), aes(x=as.factor(tobac), y=num_of_drinks, fill=as.factor(tobac))) + 
    geom_boxplot()+
  scale_fill_discrete(name="tobacco or cigarettes use")+
  labs(x = "Have you used tobacco or cigarettes?", y = "Number of drinks per month")+
  scale_y_continuous(limits=c(0,100))

# ggplot(subset(df_simple,!is.na(mom_heavy_drinker)), aes(x=as.factor(mom_heavy_drinker), y=num_of_drinks, fill=as.factor(mom_heavy_drinker))) + geom_boxplot()+
#   scale_fill_discrete(name="Happiness")+
#   labs(x = "Mom is a heavy drinker", y = "Number of drinks per month")+
#   scale_y_continuous(limits=c(0,100))

ggplot(subset(df_simple,!is.na(max_par_edu)), aes(x=as.factor(max_par_edu), y=num_of_drinks, fill=as.factor(max_par_edu))) + geom_boxplot()+
  scale_fill_discrete(name="Higher Parent education", labels=c("DK","someHS","HS","some College", "College"))+
  labs(x = "Higher Parent education", y = "Number of drinks per month")+
  scale_y_continuous(limits=c(0,100))+
  scale_x_discrete(labels=c("DK","someHS","HS","some College", "College"))
  

```


### Modeling

## whether or not to use offset
## poisson distribution, truncated?
## dont know the student ID, so hard to do time series problem
## find proxy for heavy drinking (# drinks per month?)
## missing values could be found in codebook

---------------------------------------
## Logistic regression on people who never drink
###-------------------- 1993
```{r}
library(dplyr)
library(knitr)
devtools::install_github("haozhu233/kableExtra")
library("kableExtra")
load("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/df.rdata")
library(BMA)
df<- df[,-2]
df_ref<- df %>% dplyr::select(-c(age_15_17,subfree_on_housing, no_roommate,school_disc_never, happy, single, religion_none, max_parent_edu_DK, hispanic))

des_mat = model.matrix(lm(drinks_binary ~ ., data = df_ref))
des_mat<- des_mat[,-1]
des_mat<- cbind(drinks_binary = df_ref$drinks_binary, des_mat)
des_mat<- as.data.frame(des_mat)
###---------------------------- normal logistic regression
mylogit <- glm(formula = drinks_binary ~., data = des_mat, family = "binomial")
summary(mylogit)
#exp(coef(mylogit))
### ------------------------------stepwise logistic (maybe variable selection)
library(dplyr)
model_stepwise <- glm(formula = drinks_binary ~., data = des_mat, family = "binomial") %>% stepAIC(trace = FALSE)
save(model_stepwise, file="model_stepwise.rdata")
summary(model_stepwise)

odds_mean<- exp(summary(model_stepwise)$coefficients[, "Estimate"])
odds_lb <- exp(-2 * summary(model_stepwise)$coefficients[, "Std. Error"])
odds_ub <- exp(2 * summary(model_stepwise)$coefficients[, "Std. Error"])
probs_lb <- odds_lb / (1 + odds_lb); probs_ub <- odds_ub / (1 + odds_ub);
probs_mean<- odds_mean / (1 + odds_mean);
library(gtools)
sig_level<- stars.pval(summary(model_stepwise)$coefficients[,4])
# kable(cbind.data.frame("Lower bound" = probs_lb,
#                               "Mean" = probs_mean,
#                               "Upper bound" = probs_ub
#                               ),
#              format = "latex", digits = 3)
library(xtable)
xtable(cbind.data.frame("Lower bound" = probs_lb,
                              "Mean" = probs_mean,
                              "Upper bound" = probs_ub,
                        "Significance level" = sig_level))
                              

#---------------------------BMA (giving me error)
#glm_0<- bic.glm(df_simple[,-c(1,2)], df_simple[,1], glm.family="binomial", factor.type=FALSE)
#summary(glm_0)
#imageplot.bma(glm_0)

###-------------------------------Bayes logistic (similar results as freq)
library(arm)
df_simple_bayes<- as.data.frame(df_simple[,-2])
fit <- bayesglm(formula = drinks_binary ~., data= des_mat, family="binomial")
summary(fit)

# library(glmnet)
# df_simple_glmnet<- as.data.frame(df_simple[,-2])
# x <- as.matrix(df_simple_glmnet[,-1])
# x <- model.matrix( ~ -1+., df_simple_glmnet[,-1])
# # Convert the outcome (class) to a numerical variable
# y <- df_simple_glmnet[,1]
# 
# cv.lasso <- cv.glmnet(des_mat, y, alpha = 1)
# plot(cv.lasso)
# # Fit the final model on the training data
# model <- glmnet(x, y, alpha = 1,
#                 lambda = cv.lasso$lambda.min)
# # Display regression coefficients
# coef(model)
```

### negative binomial regression

```{r}
#--------------------------------- factored dataset
df_nb_true0<- df_simple[(df_simple$num_of_drinks !=0 & df_simple$df.drinks_binary !=0),]

df_nb_true0$num_of_drinks<- ceiling(as.numeric(df_nb_true0$num_of_drinks))
hist(df_nb_true0$num_of_drinks)
mean(df_nb_true0$num_of_drinks); var(df_nb_true0$num_of_drinks)
### Since variance is a lot larger than mean, we use negative binomial model
#----------------------------------------

#---------------------------------If using the indicator dataset
load("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/df.rdata")
df_nb_true0<- df[(df$num_of_drinks !=0 & df$drinks_binary !=0),]

df_nb_true0$num_of_drinks<- ceiling(as.numeric(df_nb_true0$num_of_drinks))
hist(df_nb_true0$num_of_drinks)
mean(df_nb_true0$num_of_drinks); var(df_nb_true0$num_of_drinks)

df_nb_true0<- df_nb_true0[,-1]
df_nb_true0<- df_nb_true0 %>% dplyr::select(-c(age_15_17,subfree_on_housing, no_roommate,school_disc_never, happy, single, religion_none, max_parent_edu_DK, hispanic))

des_mat = model.matrix(lm(num_of_drinks ~ ., data = df_nb_true0))
des_mat<- des_mat[,-1]
des_mat<- cbind(num_of_drinks = df_nb_true0$num_of_drinks, des_mat)
df_nb_true0_all<- as.data.frame(des_mat)

#library(VGAM)
#fit_nb<- vglm(formula = num_of_drinks ~., family = posnegbinomial(), data = df_nb_true0_all)
#summary(fit_nb)
#round(exp(coef(m2)),3)

library(MASS)
fit_nb<- glm.nb(formula = num_of_drinks ~., data = df_nb_true0_all,link = log)
summary(fit_nb)
round(exp(coef(fit_nb)),3)

odds_mean<- exp(summary(fit_nb)$coefficients[, "Estimate"])
odds_lb <- exp(-2 * summary(fit_nb)$coefficients[, "Std. Error"])
odds_ub <- exp(2 * summary(fit_nb)$coefficients[, "Std. Error"])
probs_lb <- odds_lb / (1 + odds_lb); probs_ub <- odds_ub / (1 + odds_ub);
probs_mean<- odds_mean / (1 + odds_mean);
library(gtools)
sig_level<- stars.pval(summary(fit_nb)$coefficients[,4])
# kable(cbind.data.frame("Lower bound" = probs_lb,
#                               "Mean" = probs_mean,
#                               "Upper bound" = probs_ub
#                               ),
#              format = "latex", digits = 3)
library(xtable)
xtable(cbind.data.frame("Lower bound" = probs_lb,
                              "Mean" = probs_mean,
                              "Upper bound" = probs_ub,
                        "Significance level" = sig_level))
                              

list(residual.deviance= deviance(fit_nb),
     residual.degrees.of.freedom = df.residual(fit_nb),
     chisq.p.value= pchisq(deviance(fit_nb), df.residual(fit_nb), lower = F)
     )

### pvalue pretty small

#------------------- Using factored data
#fit_nb<- glm.nb(formula = num_of_drinks ~., data = df_nb_true0,link = log)
#summary(fit_nb)

##gof ... 
#df_simple$num_drink_true0<- ifelse(df_simple$num_of_drinks ==0 & df_simple$df.drinks_binary ==0, 0, df_simple$num_of_drinks)

```

###----------------------------------------------------------------------------- 2001

### logistic on people who never drink 
```{r}
load("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/df_2001.rdata")
df<- df_2001
library(BMA)
df<- df[,-2]
df_ref<- df %>% dplyr::select(-c(age_15_17,subfree_on_housing, weird_roomate, happy, single, religion_none, max_parent_edu_DK))

des_mat = model.matrix(lm(drinks_binary ~ ., data = df_ref))
des_mat<- des_mat[,-1]
des_mat<- cbind(drinks_binary = df_ref$drinks_binary, des_mat)
des_mat<- as.data.frame(des_mat)
###---------------------------- normal logistic regression
# mylogit <- glm(formula = drinks_binary ~., data = des_mat, family = "binomial")
# summary(mylogit)
# exp(coef(mylogit))
### ------------------------------stepwise logistic (maybe variable selection)
library(dplyr)
model_stepwise <- glm(formula = drinks_binary ~., data = des_mat, family = "binomial") %>% stepAIC(trace = FALSE)
save(model_stepwise, file="model_stepwise.rdata")
summary(model_stepwise)

odds_mean<- exp(summary(model_stepwise)$coefficients)
odds_lb <- exp(-2 * summary(model_stepwise)$coefficients[, "Std. Error"])
odds_ub <- exp(2 * summary(model_stepwise)$coefficients[, "Std. Error"])
probs_lb <- odds_lb / (1 + odds_lb); probs_ub <- odds_ub / (1 + odds_ub);
probs_mean<- odds_mean / (1 + odds_mean);
knitr::kable(cbind.data.frame("Lower bound" = probs_lb,
                              "Mean" = probs_mean,
                              "Upper bound" = probs_ub
                              ),
             format = "latex", digits = 3)

```

### negative binomial regression

```{r}
#--------------------------------- factored dataset
df_nb_true0<- df_simple[(df_simple$num_of_drinks !=0 & df_simple$df.drinks_binary !=0),]

df_nb_true0$num_of_drinks<- ceiling(as.numeric(df_nb_true0$num_of_drinks))
hist(df_nb_true0$num_of_drinks)
mean(df_nb_true0$num_of_drinks); var(df_nb_true0$num_of_drinks)
### Since variance is a lot larger than mean, we use negative binomial model
#----------------------------------------

#---------------------------------If using the indicator dataset
load("C:/Users/XJ/OneDrive - Duke University/STA-723/Case-Study-3-team-2/df.rdata")
df_nb_true0<- df[(df$num_of_drinks !=0 & df$drinks_binary !=0),]

df_nb_true0$num_of_drinks<- ceiling(as.numeric(df_nb_true0$num_of_drinks))
hist(df_nb_true0$num_of_drinks)
mean(df_nb_true0$num_of_drinks); var(df_nb_true0$num_of_drinks)

df_nb_true0<- df_nb_true0[,-1]
des_mat = model.matrix(lm(num_of_drinks ~ ., data = df_nb_true0))
des_mat<- des_mat[,-1]
des_mat<- cbind(num_of_drinks = df_nb_true0$num_of_drinks, des_mat)
df_nb_true0_all<- as.data.frame(des_mat)

#library(VGAM)
#fit_nb<- vglm(formula = num_of_drinks ~., family = posnegbinomial(), data = df_nb_true0_all)
#summary(fit_nb)
#round(exp(coef(m2)),3)

library(MASS)
fit_nb<- glm.nb(formula = num_of_drinks ~., data = df_nb_true0_all,link = log)
summary(fit_nb)
round(exp(coef(fit_nb)),3)

odds_mean<- exp(summary(fit_nb)$coefficients)
odds_lb <- exp(-2 * summary(fit_nb)$coefficients[, "Std. Error"])
odds_ub <- exp(2 * summary(fit_nb)$coefficients[, "Std. Error"])
probs_lb <- odds_lb / (1 + odds_lb); probs_ub <- odds_ub / (1 + odds_ub);
probs_mean<- odds_mean / (1 + odds_mean);
knitr::kable(cbind.data.frame("Lower bound" = probs_lb,
                              "Mean" = probs_mean,
                              "Upper bound" = probs_ub
                              ),
             format = "latex", digits = 3)

list(residual.deviance= deviance(fit_nb),
     residual.degrees.of.freedom = df.residual(fit_nb),
     chisq.p.value= pchisq(deviance(fit_nb), df.residual(fit_nb), lower = F)
     )

### pvalue pretty small

#------------------- Using factored data
#fit_nb<- glm.nb(formula = num_of_drinks ~., data = df_nb_true0,link = log)
#summary(fit_nb)

##gof ... 
#df_simple$num_drink_true0<- ifelse(df_simple$num_of_drinks ==0 & df_simple$df.drinks_binary ==0, 0, df_simple$num_of_drinks)

```

